The \dealii{} Library, Version 8.5

### 2017-03-02 8.5/deal85.tex
Add my complete address.
List major news.

\hypersetup{
  pdfauthor={Wolfgang Bangerth, Timo Heister},
  pdftitle={The deal.II Library, Version 8.5, 2016},
}

@@

\title{The \dealii{} Library, Version 8.5}
\author[1]{Wolfgang Bangerth}
\affil[1]{xxx,
    {\texttt{bangerth@math.tamu.edu}}}    
\author[2]{Timo Heister}
\affil[2]{Mathematical Sciences,
  O-110 Martin Hall.
  Clemson University.
  Clemson, SC 29634, USA,
  {\texttt{heister@clemson.edu}}}

@@

\dealii{} version 8.5.0 was released March 11, 2017. This paper provides an
overview of the new features of this release and serves as a citable
reference for the \dealii{} software library version 8.5. \dealii{} is an
object-oriented finite element library used around the world in the
development of finite element solvers. It is available for free under the
GNU Lesser General Public License (LGPL) from the \dealii{} homepage at
\url{http://www.dealii.org/}.

The major changes of this release are:
\begin{itemize}
\item 
\item More than 140 other features and bugfixes.
\end{itemize}
The more important ones of these will be detailed in the following section.
Information on how to cite \dealii{} is provided in Section \ref{sec:cite}.

@@

This release of \dealii{} contains a number of large and significant changes
that will be discussed in the following sections. It of course also contains a
vast number of smaller changes and added functionality; the details of these
can be found
\href{https://www.dealii.org/8.4.0/doxygen/deal.II/changes_between_8_3_and_8_4.html}{in the file that lists all changes for this release} (see \cite{changes84})
and that is linked to from the web site of each release as well as the
release announcement.

@@

@@

@@

The
\href{https://www.dealii.org/8.4.0/doxygen/deal.II/changes_between_8_3_and_8_4.html}{file
  that lists all changes for this release} (see \cite{changes84}) lists another 18
incompatible changes, but none of these should in fact be visible in
typical user codes. Some remove previously deprecated classes and
functions, and the majority change internal interfaces that are not
typically used in user codes.

>>>>

@@

%
% Author list -- please add yourself in both places below (in
%                alphabetical order) if you think that your
%                contributions to the last release warrant this
%

\hypersetup{
  pdfauthor={
    Wolfgang Bangerth,
    Timo Heister
  },
  pdftitle={The deal.II Library, Version 8.5, 2017},
}

\title{The \dealii{} Library, Version 8.5}

\author[1]{Wolfgang Bangerth}
\affil[1]{Department of Mathematics, Colorado State University, Fort
  Collins, CO 80523-1874, USA.
    {\texttt{bangerth@colostate.edu}}}

\author[2]{Timo Heister}
\affil[2]{Mathematical Sciences,
  O-110 Martin Hall,
  Clemson University,
  Clemson, SC 29634, USA.
  {\texttt{heister@clemson.edu}}}

@@

\marginpar{Update date}
\dealii{} version 8.5.0 was released March 11, 2017. This paper provides an
overview of the new features of this release and serves as a citable
reference for the \dealii{} software library version 8.5. \dealii{} is an
object-oriented finite element library used around the world in the
development of finite element solvers. It is available for free under the
GNU Lesser General Public License (LGPL) from the \dealii{} homepage at
\url{http://www.dealii.org/}.

The major changes of this release are:
\begin{itemize}
\item CellDataStorage class

\item MappingManifold

\item Trilinos linear operators?

\item Physics module

\item FE\_Enriched

\item FESeries namespace, use in step-27

\item step-57, step-55, step-56

\item step-44 improvements

\item step-37 parallel improvements

\item New code gallery codes demonstrating (i) quasi-static visco-elastic
  material behavior, (ii) multiphase Navier-Stokes flow, (iii) the
  evolution of global-scale topography on planetary bodies, (iv)
  goal-oriented elastoplasticity.

\item More than 230 other features and bugfixes.
\end{itemize}
The more important ones of these will be detailed in the following section.
Information on how to cite \dealii{} is provided in Section \ref{sec:cite}.

@@

This release of \dealii{} contains a number of large and significant changes
that will be discussed in the following sections. It of course also contains a
vast number of smaller changes and added functionality; the details of these
can be found
\href{https://www.dealii.org/8.5.0/doxygen/deal.II/changes_between_8_4_and_8_5.html}{in the file that lists all changes for this release} (see \cite{changes84})
and that is linked to from the web site of each release as well as the
release announcement.

@@

Other things we could talk about:
PVS static checker, coverity, ...

GridReordering rewrite

No longer use features of C++ deprecated with C++11/14/17
Move operators

Python bindings

@@

Switch default of Lagrange elements to Gauss-Lobatto

@@

No long double instantiations any more

ParameterGUI moved to separate repo

The
\href{https://www.dealii.org/8.5.0/doxygen/deal.II/changes_between_8_4_and_8_5.html}{file
  that lists all changes for this release} (see \cite{changes84})
lists another around 20
incompatible changes, but none of these should in fact be visible in
typical user codes. Some remove previously deprecated classes and
functions, and the majority change internal interfaces that are not
typically used in user codes.
